Data preparation Study 3 - Merit Scale

### 2021-06-03 processing/preparation_study3.rmd
Estudio 3
Se ajusta preparación del S3, se crean 2 bases data_s3_conv y data_s3_inv, para convergencia e invarianza.

Se ajusta paper_s3, reproducible.

---
title: "Data preparation"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
css: "../input/bib/style.css"
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

```{r eval=FALSE, include=FALSE}
rmarkdown::render(input = "production/prod_prep-data-A.Rmd",output_format = "html_document",output_dir = "production/");browseURL(url = "production/prod_prep-data-A.html")
```

```{r include=FALSE}
knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

load packages
```{r}
library(sjPlot)
library(dplyr)
library(tidyr)
library(lavaan)
library(stargazer)
library(corrplot)
library(psych)
library(knitr)
library(kableExtra)
library(summarytools)
library(sjlabelled)
library(Hmisc)
```

# Data preparation according order of the items

```{r}
w01 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola1.sav",verbose = F)
```

##  homogenize names of the items on the scale.

The items on the scale had different orders according to the order in which they were exposed to the respondents. There are three order. The first one the orders keeps together the items of the same factor. The second order then asks for perceptions and preferences regarding the same topic (i.e Distribution of resources according to efforts). In the third order, the items are presented randomly to each respondent.

```{r}
dat04 <- w01 %>% filter(Intro==1) %>%
  select(starts_with("meritv01"),
         starts_with("meritv02"),
         starts_with("meritv03_p"),
         starts_with("FL_21_DO"))
dat04$grupo <- NA
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
dat04$grupo[dat04$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
dat04$perc_effort <- rowSums(dat04[,c(matches(match = "perc_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_talent <- rowSums(dat04[,c(matches(match = "perc_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$perc_wpart  <- rowSums(dat04[,c(matches(match = "perc_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$perc_netw   <- rowSums(dat04[,c(matches(match = "perc_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_effort <- rowSums(dat04[,c(matches(match = "pref_effort",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_talent <- rowSums(dat04[,c(matches(match = "pref_talent",vars = names(dat04)))],na.rm = TRUE)
dat04$pref_wpart  <- rowSums(dat04[,c(matches(match = "pref_wpart" ,vars = names(dat04)))],na.rm = TRUE)
dat04$pref_netw   <- rowSums(dat04[,c(matches(match = "pref_netw"  ,vars = names(dat04)))],na.rm = TRUE)
dat04[dat04==0] <- NA
dat04 <- dat04 %>% select(starts_with(match = "perc_"),starts_with(match = "pref_"),grupo) %>% na.omit()
```

## Translation of variable labels and value labels.
```{r}
label(dat04$grupo) <- "This variable classifies the interviewees according to the order in which the indicators are shown within the scale. There are three orders  of items on the scale. In the first order (group 1), questions of the same factor are then presented to them, in the second order (group 2) they were separated and in the third order (group 3) at random."
dat04$perc_effort <- set_labels(dat04$perc_effort,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$perc_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they manage to get bigger
rewards that those who strive
less."
dat04$perc_talent <- set_labels(dat04$perc_talent,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$perc_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they manage to obtain
greater rewards than those who possess
less talent."
dat04$perc_wpart <- set_labels(dat04$perc_wpart,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$perc_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have rich parents manage to get out
ahead."
dat04$perc_netw <- set_labels(dat04$perc_netw,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$perc_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
they have good contacts they manage to get out
ahead."
dat04$pref_effort <- set_labels(dat04$pref_effort,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$pref_effort) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
the more they try they should get
greater rewards than those who
they try less."
dat04$pref_talent <- set_labels(dat04$pref_talent,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$pref_talent) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Who
possess more talent they should get
greater rewards than those who possess
less talent."
dat04$pref_wpart <- set_labels(dat04$pref_wpart,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$pref_wpart) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - It's fine that those who have rich parents get ahead" 
dat04$pref_netw <- set_labels(dat04$pref_netw,  labels = c("Strongly disagree" = 1, "Disagreement" = 2, "Neither agree nor disagree"=3,"Agree"=4, "Totally agree" = 5))
label(dat04$pref_netw) <- "Thinking of Chilean society,
what measure do you find of
agree or disagree with each of
the following statements? - Is
well that those who have good
contacts get ahead."
```

```{r}
dat04 <-  dat04 %>% select(grupo, perc_effort, perc_talent, perc_wpart, perc_netw, pref_effort, pref_talent, pref_wpart , pref_netw) %>% as.data.frame()
```

```{r}
print(dfSummary(dat04, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

## Preparation of group 1: order according to the factors.

```{r}
dat01 <- dat04 %>% filter(grupo==1) %>% select(-grupo) %>%  na.omit()
```

```{r}
print(dfSummary(dat01, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

## Preparation of group 2: order according to topics (i.e Effort).

```{r}
dat02 <- dat04 %>% filter(grupo==2) %>% select(perc_effort, pref_effort, perc_talent,pref_talent, perc_wpart,pref_wpart, perc_netw, pref_netw) %>% na.omit()
```

```{r}
print(dfSummary(dat02, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

## Preparation of group 3: randomized order.

```{r}
dat03 <- dat04 %>% filter(grupo==3) %>% select(-grupo) %>%  na.omit()
```

```{r}
print(dfSummary(dat03, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

## save data
```{r}
save(dat01,file = "input/data/proc/dat01.RData")
save(dat02,file = "input/data/proc/dat02.RData")
save(dat03,file = "input/data/proc/dat03.RData")
save(dat04,file = "input/data/proc/dat04.RData")
```

# Longitudinal data

load data
```{r}
w01 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola1.sav",verbose = F)
w02 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola2.sav",verbose = F)
w03 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola3.sav",verbose = F)
```

@@

```{r}
w01c <- w01b
w01c$grupo <- NA
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
w01c$perc_effort_w1 <- rowSums(w01c[,c(matches(match = "perc_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_talent_w1 <- rowSums(w01c[,c(matches(match = "perc_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_wpart_w1  <- rowSums(w01c[,c(matches(match = "perc_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$perc_netw_w1   <- rowSums(w01c[,c(matches(match = "perc_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_effort_w1 <- rowSums(w01c[,c(matches(match = "pref_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_talent_w1 <- rowSums(w01c[,c(matches(match = "pref_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_wpart_w1  <- rowSums(w01c[,c(matches(match = "pref_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_netw_w1   <- rowSums(w01c[,c(matches(match = "pref_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c[w01c==0] <- NA
w01c <- w01c %>% select(grupo,
                        perc_effort_w1,perc_talent_w1,perc_wpart_w1,perc_netw_w1,
                        pref_effort_w1,pref_talent_w1,pref_wpart_w1,pref_netw_w1,
                        sexo_w1=sexo,edad_w1=edad,edcep_w1=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w01c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

@@

```{r}
w03c <- w03b
w03c <- w03c %>% rename(perc_effort_w3=meritv03_perc_effort,
                        perc_talent_w3=meritv03_perc_talent,
                        perc_wpart_w3 =meritv03_perc_wpart,
                        perc_netw_w3  =meritv03_perc_netw,
                        pref_effort_w3=meritv03_pref_effort,
                        pref_talent_w3=meritv03_pref_talent,
                        pref_wpart_w3 =meritv03_pref_wpart,
                        pref_netw_w3  =meritv03_pref_netw)
w03c <- w03c %>% select(perc_effort_w3,perc_talent_w3,perc_wpart_w3,perc_netw_w3,
                        pref_effort_w3,pref_talent_w3,pref_wpart_w3,pref_netw_w3,
                        sexo_w3=sexo,edad_w3=edad,edcep_w3=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w03c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
wide01 <- inner_join(x = w01c,y = w02c, by = "ID") # Solamente nos quedamos con casos en ambas olas
dim(wide01) #en w01 y w02
```

```{r}
wide02 <- inner_join(x = wide01,y = w03c, by = "ID") # Solamente nos quedamos con casos en ambas olas
dim(wide02) #en w01, w02 y w03
```

@@

```{r}
save(wide01,file = "input/data/proc/datawide.RData")
save(wide02,file = "input/data/proc/datawide_123.RData")
```

# Wide to long data

```{r}
library(datasets)
library(data.table)
wide <- setDT(wide02)
long01<- melt(wide,variable.name = "wave",
              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
                                       "^sexo_","^edad_","^edcep_"),
              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                             "pref_effort","pref_talent","pref_wpart","pref_netw",
                             "sexo","edad","edcep"))
```

```{r}
#save(long01,file = "input/data/proc/datalong.RData")
```

# Factorial survey data:

@@

```{r}
# fs01 <- sjlabelled::read_spss("input/data/original/factorial_ola2.sav",verbose = F)
load(file = "input/data/original/factorial_ola2.RData")
```

@@

```{r}
pov_fs<-bind_rows(fs02,w01fs) %>%
  set_label(label = get_label(fs02)) %>%
  set_labels(labels = get_labels(fs02))
```

```{r}
save(pov_fs,file = "input/data/proc/pov01_fact02.RData")
```

>>>>

---
title: "Data preparation Study 3 - Merit Scale"
date: "`r format(Sys.time(), '%A %d %B %Y %X')`"
output:
  bookdown::html_document2:
    number_sections: true
    toc: true
    toc_float:
        collapsed: false
    toc_depth: 2
    code_folding: "hide"
editor_options:
  chunk_output_type: console
---

```{r include=FALSE}
# Knitr options

knitr::opts_chunk$set(warning = FALSE,message = FALSE, cache = FALSE,results = "hold")
knitr::opts_knit$set(root.dir = "../")
options(scipen=999)
rm(list=ls())
options(knitr.kable.NA = '')
```

This is the preparation code of the data for Study 3:  Additional validity analyses. The prepared data is `data_s3_conv.RData` in "Convergence section" and `data_s3_conv.RData` in "Invariance section"

# Convergence

## Libraries
```{r}
pacman::p_load(haven, sjPlot, dplyr, mice, lavaan, stargazer, corrplot, polycor, knitr, kableExtra, summarytools, sjlabelled)
```

## Load original data

```{r}
dat04w3 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola3.sav",verbose = F)
dim(data) 
```

## Create Perceptions and Preferences for Meritocracy (PPM-S) factor scores

The following code creates new variables corresponding to the four dimensions of the PPM scale. Based on the measurement model, four factorial scores are created. To retrieve cases the "mice" function is used

```{r results='hide'}
dat04w3

dat04w3$meritv03_perc_effort <- as.numeric(dat04w3$meritv03_perc_effort)
dat04w3$meritv03_perc_talent <- as.numeric(dat04w3$meritv03_perc_talent)
dat04w3$meritv03_perc_netw <- as.numeric(dat04w3$meritv03_perc_netw)
dat04w3$meritv03_perc_wpart <- as.numeric(dat04w3$meritv03_perc_wpart)
dat04w3$meritv03_pref_effort <- as.numeric(dat04w3$meritv03_pref_effort)
dat04w3$meritv03_pref_talent <- as.numeric(dat04w3$meritv03_pref_talent)
dat04w3$meritv03_pref_wpart <- as.numeric(dat04w3$meritv03_pref_wpart)
dat04w3$meritv03_pref_netw <- as.numeric(dat04w3$meritv03_pref_netw)

model04 <- '
perc_merit =~  meritv03_perc_effort + meritv03_perc_talent
perc_nmerit=~ meritv03_perc_wpart + meritv03_perc_netw
pref_merit =~ meritv03_pref_effort + meritv03_pref_talent
pref_nmerit=~ meritv03_pref_wpart + meritv03_pref_netw'

# generate 5 multiple complete datasets
out <- mice(dat04w3[23:30], m = 5)

D1 <- complete(out, 1)
D2 <- complete(out, 2)
D3 <- complete(out, 3)
D4 <- complete(out, 4)
D5 <- complete(out, 5)

# fit model for each complete dataset
fit1 <- cfa(model04, data = D1)
fit2 <- cfa(model04, data = D2)
fit3 <- cfa(model04, data = D3)
fit4 <- cfa(model04, data = D4)
fit5 <- cfa(model04, data = D5)

# predict scores for all models
p1 <- predict(fit1)
p2 <- predict(fit2)
p3 <- predict(fit3)
p4 <- predict(fit4)
p5 <- predict(fit5)

# compute 'average' across 5 sets of scores:
scores <- (p1 + p2 + p3 + p4 + p5) / 5

#Generate factor scores
scores_dat = as.data.frame(scores)

# Adaptar base para agregar factor scores (sacar todos NA)
dat04w3 = dat04w3[rowSums(is.na(dat04w3[23:28])) != 5, ]

# Merge with factor scores
dat04w3 = cbind(dat04w3, scores)

# Check
stargazer(dat04w3[, 78:81], type = "text")

```

## Create The Neoliberal Beliefs Inventory (NBI) factor scores

The following code creates new variables corresponding to the four dimensions of the NBI scale. Based on the measurement model, four factorial scores are created. To retrieve cases the "mice" function is used
```{r results='hide'}
datnbmerit <- dat04w3 %>% select(nb_merit_1,
nb_merit_2,
nb_merit_3,
nb_merit_4,
nb_merit_5,
nb_merit_6,
nb_merit_7,
nb_merit_8)
psych::alpha(datnbmerit)

dat04w3$nb_merit_1 <- as.numeric(dat04w3$nb_merit_1)
dat04w3$nb_merit_2 <- as.numeric(dat04w3$nb_merit_2)
dat04w3$nb_merit_3 <- as.numeric(dat04w3$nb_merit_3)
dat04w3$nb_merit_4 <- as.numeric(dat04w3$nb_merit_4)
dat04w3$nb_merit_5 <- as.numeric(dat04w3$nb_merit_5)
dat04w3$nb_merit_6 <- as.numeric(dat04w3$nb_merit_6)
dat04w3$nb_merit_7 <- as.numeric(dat04w3$nb_merit_7)
dat04w3$nb_merit_8 <- as.numeric(dat04w3$nb_merit_8)

model04 <- '
nbmerit =~  nb_merit_1+
nb_merit_2+
nb_merit_3+
nb_merit_4+
nb_merit_5+
nb_merit_6+
nb_merit_7'

# generate 5 multiple complete datasets
out <- mice(dat04w3[57:64], m = 5)

D1 <- complete(out, 1)
D2 <- complete(out, 2)
D3 <- complete(out, 3)
D4 <- complete(out, 4)
D5 <- complete(out, 5)

# fit model for each complete dataset
fit1 <- cfa(model04, data = D1)
fit2 <- cfa(model04, data = D2)
fit3 <- cfa(model04, data = D3)
fit4 <- cfa(model04, data = D4)
fit5 <- cfa(model04, data = D5)

# predict scores for all models
p1 <- predict(fit1)
p2 <- predict(fit2)
p3 <- predict(fit3)
p4 <- predict(fit4)
p5 <- predict(fit5)

# compute 'average' across 5 sets of scores:
scores <- (p1 + p2 + p3 + p4 + p5) / 5

#Generate factor scores
scores_dat = as.data.frame(scores)

# Adaptar base para agregar factor scores (sacar todos NA)
dat04w3 = dat04w3[rowSums(is.na(dat04w3[57:64])) != 5, ]

# Merge with factor scores
dat04w3 = cbind(dat04w3, scores)

data_s3_conv <- dat04w3 %>% select(nbmerit, perc_merit,pref_merit,perc_nmerit,pref_nmerit,get_ah_1, get_ah_5) %>% na.omit()

```

## Labels

### Variable labels

Created variables are labeled and described

```{r}

set_label(data_s3_conv$nbmerit)  <- "Personal wherewithal - NBI"
set_label(data_s3_conv$perc_merit)  <- "Meritocratic perception"
set_label(data_s3_conv$pref_merit)   <- "Meritocratic preferences"
set_label(data_s3_conv$perc_wpart)    <- "Unmeritocratic perception"
set_label(data_s3_conv$pref_nmerit)  <-  "Unmeritocratic preferences"

set_label(data_s3_conv$get_ah_1)  <- "Importance of a rich family to get ahead"
set_label(data_s3_conv$get_ah_5)   <- "Importance of hard work to get ahead"

sjmisc::descr(data_s3_conv)

```

## Final summary
```{r}
sjmisc::descr(data_s3_conv,
      show = c("label","range", "mean", "sd", "NA.prc", "n"))%>%
      kable(.,"markdown")

print(dfSummary(data_s3_conv, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")

```

## save data

```{r}

save(data_s3_conv,file = "input/data/proc/data_s3_conv.RData")
```

# Invariance

## Libraries
```{r}
pacman::p_load(haven, sjPlot, dplyr, lavaan, stargazer, corrplot, knitr, kableExtra, summarytools, sjlabelled,Hmisc,psych,tidyr)

```

## Load longitudinal data

```{r}
w01 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola1.sav",verbose = F)
w02 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola2.sav",verbose = F)
w03 <- sjlabelled::read_spss("input/data/original/Estudio_3_ola3.sav",verbose = F)
```

@@

A variable is created to indicate the order in which the items on the PPM scale are presented. The variables are renamed and those of interest are selected. The results are described.
```{r}
w01c <- w01b
w01c$grupo <- NA
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v01==1] <- 1
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v02==1] <- 2
w01c$grupo[w01c$FL_21_DO_merit_perc_pref_julio19v03==1] <- 3
w01c$perc_effort_w1 <- rowSums(w01c[,c(matches(match = "perc_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_talent_w1 <- rowSums(w01c[,c(matches(match = "perc_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$perc_wpart_w1  <- rowSums(w01c[,c(matches(match = "perc_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$perc_netw_w1   <- rowSums(w01c[,c(matches(match = "perc_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_effort_w1 <- rowSums(w01c[,c(matches(match = "pref_effort",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_talent_w1 <- rowSums(w01c[,c(matches(match = "pref_talent",vars = names(w01c)))],na.rm = TRUE)
w01c$pref_wpart_w1  <- rowSums(w01c[,c(matches(match = "pref_wpart" ,vars = names(w01c)))],na.rm = TRUE)
w01c$pref_netw_w1   <- rowSums(w01c[,c(matches(match = "pref_netw"  ,vars = names(w01c)))],na.rm = TRUE)
w01c[w01c==0] <- NA
w01c <- w01c %>% select(grupo,
                        perc_effort_w1,perc_talent_w1,perc_wpart_w1,perc_netw_w1,
                        pref_effort_w1,pref_talent_w1,pref_wpart_w1,pref_netw_w1,
                        sexo_w1=sexo,edad_w1=edad,edcep_w1=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w01c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

A variable is created to indicate the treatment to which the respondent was exposed. The variables are renamed and those of interest are selected. The results are described.

@@

The variables of the PPM scale are renamed indicating the wave. Those of interest are selected. The results are described.
```{r}
w03c <- w03b
w03c <- w03c %>% rename(perc_effort_w3=meritv03_perc_effort,
                        perc_talent_w3=meritv03_perc_talent,
                        perc_wpart_w3 =meritv03_perc_wpart,
                        perc_netw_w3  =meritv03_perc_netw,
                        pref_effort_w3=meritv03_pref_effort,
                        pref_talent_w3=meritv03_pref_talent,
                        pref_wpart_w3 =meritv03_pref_wpart,
                        pref_netw_w3  =meritv03_pref_netw)
w03c <- w03c %>% select(perc_effort_w3,perc_talent_w3,perc_wpart_w3,perc_netw_w3,
                        pref_effort_w3,pref_talent_w3,pref_wpart_w3,pref_netw_w3,
                        sexo_w3=sexo,edad_w3=edad,edcep_w3=edcep, ID)
#-----------------------------------------------------------------------#
print(dfSummary(w03c, valid.col = FALSE, graph.magnif = 0.75),
      max.tbl.height = 300, method = "render")
```

@@

```{r}
wide01 <- inner_join(x = w01c,y = w02c, by = "ID") 
dim(wide01) #en w01 y w02
```

```{r}
wide02 <- inner_join(x = wide01,y = w03c, by = "ID") 
dim(wide02) #en w01, w02 y w03
```

@@

```{r}
#save(wide01,file = "input/data/proc/datawide.RData")
#save(wide02,file = "input/data/proc/datawide_123.RData")
```

## Wide to long data

```{r}
library(datasets)
library(data.table)
wide <- setDT(wide02)
long01<- melt(wide,variable.name = "wave",
              measure = patterns("^perc_effort_","^perc_talent_","^perc_wpart_","^perc_netw_",
                                       "^pref_effort_","^pref_talent_","^pref_wpart_","^pref_netw_",
                                       "^sexo_","^edad_","^edcep_"),
              value.name = c("perc_effort","perc_talent","perc_wpart","perc_netw",
                             "pref_effort","pref_talent","pref_wpart","pref_netw",
                             "sexo","edad","edcep"))
#save(long01,file = "input/data/proc/datalong.RData")

```

## Factorial survey data:

@@

```{r}
# fs01 <- sjlabelled::read_spss("input/data/original/factorial_ola2.sav",verbose = F)
load(file = "papelera/input/data/original/factorial_ola2.RData") 
```

@@

```{r}
data_s3_inv<-bind_rows(fs02,w01fs) %>%
  set_label(label = get_label(fs02)) %>%
  set_labels(labels = get_labels(fs02))
```

```{r}
save(data_s3_inv,file = "input/data/proc/data_s3_inv.RData")
```
